---
title: "R Notebook"
output: html_notebook
---

```{r setup}
library(readr)
library(dplyr)
library(ggplot2)
library(plotly)
library(boot)
library(scales)
library(tidyr)
```

```{r}
file_path <- "/Users/maxwoolf/Dropbox/PythonProjects/keras-cntk-benchmark/logs/"
```


```{r}
framework_colors <- c(CNTK="#2980b9",TensorFlow="#c0392b")
```

# IMDb

## imdb_bidirectional_lstm

```{r}
df_imdb_bi_cntk <- read_csv(paste0(file_path, "imdb_bidirectional_lstm_cntk.csv"))
df_imdb_bi_tf <- read_csv(paste0(file_path, "imdb_bidirectional_lstm_tensorflow.csv"))
```

Test the bootstrapping functionality via `boot`.

```{r}
elapsed_mean <- function(data, indices){
  d <- data[indices,]
  mean(d$elapsed)
}

(df_imdb_bi_cntk %>% boot(elapsed_mean, 1000) %>% boot.ci(type="bca"))$bca[4:5]
```

### Test Acc

```{r}
df <- df_imdb_bi_cntk %>% mutate(framework = 'CNTK', epoch = epoch + 1) %>% union(
        df_imdb_bi_tf %>% mutate(framework = 'TensorFlow', epoch = epoch + 1)
)

df
```


```{r}
plot <- ggplot(df, aes(epoch, val_acc, color=framework)) +
          geom_line() +
          geom_point(size=2) + 
          theme_minimal(base_family="Source Sans Pro") +
          scale_y_continuous(labels = percent) +
          scale_color_manual(values=framework_colors) +
          labs(title = "Performance of Bidirectional LSTM Approach on IMDb Data",
               x = "Epoch",
               y = "Test Accuracy (Higher is Better)",
               color = "")

plot
plot %>% ggplotly(width="100%")
```

### Speed

```{r}
df_speed <- df %>% group_by(framework) %>%
  do({
    boot <- boot.ci(boot(., elapsed_mean, 1000), type="bca")$bca
    data.frame(
      mean = mean(.$elapsed),
      low_ci = boot[4],
      high_ci = boot[5]
    )
    }) %>%
  ungroup() %>%
  mutate(framework = factor(framework))

df_speed
```


```{r}
plot <- ggplot(df_speed, aes(x=framework, y=mean, ymin=low_ci, ymax=high_ci, fill=framework)) +
          geom_bar(stat="identity", width=0.25) +
          geom_errorbar(width = 0.125) +
          theme_minimal(base_family="Source Sans Pro") +
          scale_fill_manual(values=framework_colors) +
          labs(title = "Speed of Bidirectional LSTM Approach on IMDb Data",
               x = "Keras Backend",
               y = "Average Runtime per Epoch (seconds)",
               fill = "")

plot
plot %>% ggplotly(tooltip=c("x", "y"), width="100%")
```

CNTK is **`r (df_speed$mean[2] / df_speed$mean[1]) %>% round(2)`**x the speed of TensorFlow.

## FastText


```{r}
df_imdb_ft_cntk <- read_csv(paste0(file_path, "imdb_fasttext_cntk.csv"))
df_imdb_ft_tf <- read_csv(paste0(file_path, "imdb_fasttext_tensorflow.csv"))
```

### Test Acc

```{r}
df <- df_imdb_ft_cntk %>% mutate(framework = 'CNTK', epoch = epoch + 1) %>% union(
        df_imdb_ft_tf %>% mutate(framework = 'TensorFlow', epoch = epoch + 1)
)

df
```


```{r}
plot <- ggplot(df, aes(epoch, val_acc, color=framework)) +
          geom_line() +
          geom_point(size=2) + 
          theme_minimal(base_family="Source Sans Pro") +
          scale_y_continuous(labels = percent) +
          scale_color_manual(values=framework_colors) +
          labs(title = "Performance of fasttext Approach on IMDb Data",
               x = "Epoch",
               y = "Test Accuracy (Higher is Better)",
               color= "")

plot %>% ggplotly()
```

### Speed

```{r}
df_speed <- df %>% group_by(framework) %>%
  do({
    boot <- boot.ci(boot(., elapsed_mean, 1000), type="bca")$bca
    data.frame(
      mean = mean(.$elapsed),
      low_ci = boot[4],
      high_ci = boot[5]
    )
    }) %>%
  ungroup() %>%
  mutate(framework = factor(framework))

df_speed
```


```{r}
plot <- ggplot(df_speed, aes(x=framework, y=mean, ymin=low_ci, ymax=high_ci, fill=framework)) +
          geom_bar(stat="identity", width=0.5) +
          geom_errorbar(width = 0.25) +
          theme_minimal(base_family="Source Sans Pro") +
          scale_fill_manual(values=framework_colors) +
          labs(title = "Speed of fasttext Approach on IMDb Data",
               x = "Keras Backend",
               y = "Average Runtime per Epoch (seconds)",
               fill="")

plot %>% ggplotly(tooltip=c("x", "y"))
```

CNTK is **`r (df_speed$mean[2] / df_speed$mean[1]) %>% round(2)`**x the speed of TensorFlow.

# MNIST

## MLP

```{r}
df_mnist_mlp_cntk <- read_csv(paste0(file_path, "mnist_mlp_cntk.csv"))
df_mnist_mlp_tf <- read_csv(paste0(file_path, "mnist_mlp_tensorflow.csv"))
```

### Test Acc

```{r}
df <- df_mnist_mlp_cntk %>% mutate(framework = 'CNTK', epoch = epoch + 1) %>% union(
        df_mnist_mlp_tf %>% mutate(framework = 'TensorFlow', epoch = epoch + 1)
)

df
```


```{r}
plot <- ggplot(df, aes(epoch, val_acc, color=framework)) +
          geom_line() +
          geom_point(size=2) + 
          theme_minimal(base_family="Source Sans Pro") +
          scale_color_manual(values=framework_colors) +
          scale_y_continuous(labels = percent) +
          labs(title = "Performance of MLP Approach on MNIST Data",
               x = "Epoch",
               y = "Test Accuracy (Higher is Better)",
               color="")

plot %>% ggplotly()
```

### Speed

```{r}
df_speed <- df %>% group_by(framework) %>%
  do({
    boot <- boot.ci(boot(., elapsed_mean, 1000), type="bca")$bca
    data.frame(
      mean = mean(.$elapsed),
      low_ci = boot[4],
      high_ci = boot[5]
    )
    }) %>%
  ungroup() %>%
  mutate(framework = factor(framework))

df_speed
```


```{r}
plot <- ggplot(df_speed, aes(x=framework, y=mean, ymin=low_ci, ymax=high_ci, fill=framework)) +
          geom_bar(stat="identity", width=0.5) +
          geom_errorbar(width = 0.25) +
          theme_minimal(base_family="Source Sans Pro") +
          scale_fill_manual(values=framework_colors) +
          labs(title = "Speed of MLP Approach on MNIST Data",
               x = "Keras Backend",
               y = "Average Runtine per Epoch (seconds)",
               fill="")

plot %>% ggplotly(tooltip=c("x", "y"))
```

CNTK is **`r (df_speed$mean[2] / df_speed$mean[1]) %>% round(2)`**x the speed of TensorFlow.

## CNN


```{r}
df_mnist_cnn_cntk <- read_csv(paste0(file_path, "mnist_cnn_cntk.csv"))
df_mnist_cnn_tf <- read_csv(paste0(file_path, "mnist_cnn_tensorflow.csv"))
```

### Test Acc

```{r}
df <- df_mnist_cnn_cntk %>% mutate(framework = 'CNTK', epoch = epoch + 1) %>% union(
        df_mnist_cnn_tf %>% mutate(framework = 'TensorFlow', epoch = epoch + 1)
)

df
```


```{r}
plot <- ggplot(df, aes(epoch, val_acc, color=framework)) +
          geom_line() +
          geom_point(size=2) + 
          theme_minimal(base_family="Source Sans Pro") +
          scale_y_continuous(labels = percent) +
          scale_color_manual(values=framework_colors) +
          labs(title = "Performance of CNN Approach on MNIST Data",
               x = "Epoch",
               y = "Test Accuracy (Higher is Better)",
               color="")

plot %>% ggplotly()
```

### Speed

```{r}
df_speed <- df %>% group_by(framework) %>%
  do({
    boot <- boot.ci(boot(., elapsed_mean, 1000), type="bca")$bca
    data.frame(
      mean = mean(.$elapsed),
      low_ci = boot[4],
      high_ci = boot[5]
    )
    }) %>%
  ungroup() %>%
  mutate(framework = factor(framework))

df_speed
```


```{r}
plot <- ggplot(df_speed, aes(x=framework, y=mean, ymin=low_ci, ymax=high_ci, fill=framework)) +
          geom_bar(stat="identity", width=0.5) +
          geom_errorbar(width = 0.25) +
          theme_minimal(base_family="Source Sans Pro") +
          scale_fill_manual(values=framework_colors) +
          labs(title = "Speed of CNN Approach on MNIST Data",
               x = "Keras Backend",
               y = "Average Runtime per Epoch (seconds)",
               fill = "")

plot %>% ggplotly(tooltip=c("x", "y"))
```

CNTK is **`r (df_speed$mean[2] / df_speed$mean[1]) %>% round(2)`**x the speed of TensorFlow.

# CIFAR:

## CNN


```{r}
df_cifar_cnn_cntk <- read_csv(paste0(file_path, "cifar10_cnn_cntk.csv"))
df_cifar_cnn_tf <- read_csv(paste0(file_path, "cifar10_cnn_tensorflow.csv"))
```

### Test Acc

```{r}
df <- df_cifar_cnn_cntk %>% mutate(framework = 'CNTK', epoch = epoch + 1) %>% union(
        df_cifar_cnn_tf %>% mutate(framework = 'TensorFlow', epoch = epoch + 1)
)

df
```


```{r}
plot <- ggplot(df, aes(epoch, val_acc, color=framework)) +
          geom_line() +
          geom_point(size=2) + 
          theme_minimal(base_family="Source Sans Pro") +
          scale_y_continuous(labels = percent) +
          scale_color_manual(values=framework_colors) +
          labs(title = "Performance of CNN Approach on CIFAR Data",
               x = "Epoch",
               y = "Test Accuracy (Higher is Better)",
               color="")

plot %>% ggplotly()
```

### Speed

```{r}
df_speed <- df %>% group_by(framework) %>%
  do({
    boot <- boot.ci(boot(., elapsed_mean, 1000), type="bca")$bca
    data.frame(
      mean = mean(.$elapsed),
      low_ci = boot[4],
      high_ci = boot[5]
    )
    }) %>%
  ungroup() %>%
  mutate(framework = factor(framework))

df_speed
```


```{r}
plot <- ggplot(df_speed, aes(x=framework, y=mean, ymin=low_ci, ymax=high_ci, fill=framework)) +
          geom_bar(stat="identity", width=0.5) +
          geom_errorbar(width = 0.25) +
          theme_minimal(base_family="Source Sans Pro") +
          scale_fill_manual(values=framework_colors) +
          labs(title = "Speed of CNN Approach on CIFAR Data",
               x = "Keras Backend",
               y = "Average Runtime per Epoch (seconds)",
               fill = "")

plot %>% ggplotly(tooltip=c("x", "y"))
```

CNTK is **`r (df_speed$mean[2] / df_speed$mean[1]) %>% round(2)`**x the speed of TensorFlow.

# Text Generation

## CNN


```{r}
df_gen_lstm_cntk <- read_csv(paste0(file_path, "lstm_text_generation_cntk.csv"))
df_gen_lstm_tf <- read_csv(paste0(file_path, "lstm_text_generation_tensorflow.csv"))
```

### Test Acc

```{r}
df <- df_gen_lstm_cntk %>% mutate(framework = 'CNTK', epoch = epoch + 1) %>% union(
        df_gen_lstm_tf %>% mutate(framework = 'TensorFlow', epoch = epoch + 1)
)

df
```


```{r}
plot <- ggplot(df, aes(epoch, loss, color=framework)) +
          geom_line() +
          geom_point(size=2) + 
          theme_minimal(base_family="Source Sans Pro") +
          scale_color_manual(values=framework_colors) +
          labs(title = "Performance of Text Generation via LSTM",
               x = "Epoch",
               y = "Loss (Lower is Better)",
               color="")

plot %>% ggplotly()
```

### Speed

```{r}
df_speed <- df %>% group_by(framework) %>%
  do({
    boot <- boot.ci(boot(., elapsed_mean, 1000), type="bca")$bca
    data.frame(
      mean = mean(.$elapsed),
      low_ci = boot[4],
      high_ci = boot[5]
    )
    }) %>%
  ungroup() %>%
  mutate(framework = factor(framework))

df_speed
```


```{r}
plot <- ggplot(df_speed, aes(x=framework, y=mean, ymin=low_ci, ymax=high_ci, fill=framework)) +
          geom_bar(stat="identity", width=0.5) +
          geom_errorbar(width = 0.25) +
          theme_minimal(base_family="Source Sans Pro") +
          scale_fill_manual(values=framework_colors) +
          labs(title = "Speed of CNN of Text Generation via LSTM",
               x = "Keras Backend",
               y = "Average Runtime per Epoch (seconds)",
               fill = "")

plot %>% ggplotly(tooltip=c("x", "y"))
```

CNTK is **`r (df_speed$mean[2] / df_speed$mean[1]) %>% round(2)`**x the speed of TensorFlow.

## Custom Keras


```{r}
df_gen_keras_cntk <- read_csv(paste0(file_path, "text_generator_keras_cntk.csv"))
df_gen_keras_tf <- read_csv(paste0(file_path, "text_generator_keras_tensorflow.csv"))
```

### Test Acc

```{r}
df <- df_gen_keras_cntk %>% mutate(framework = 'CNTK', epoch = epoch + 1) %>% union(
        df_gen_keras_tf %>% mutate(framework = 'TensorFlow', epoch = epoch + 1)
)

df
```


```{r}
plot <- ggplot(df, aes(epoch, loss, color=framework)) +
          geom_line() +
          geom_point(size=2) + 
          theme_minimal(base_family="Source Sans Pro") +
          scale_color_manual(values=framework_colors) +
          labs(title = "Performance of Text Generation via Custom Keras Model",
               x = "Epoch",
               y = "Loss (Lower is Better)",
               color="")

plot %>% ggplotly()
```

### Speed

```{r}
df_speed <- df %>% group_by(framework) %>%
  do({
    boot <- boot.ci(boot(., elapsed_mean, 1000), type="bca")$bca
    data.frame(
      mean = mean(.$elapsed),
      low_ci = boot[4],
      high_ci = boot[5]
    )
    }) %>%
  ungroup() %>%
  mutate(framework = factor(framework))

df_speed
```


```{r}
plot <- ggplot(df_speed, aes(x=framework, y=mean, ymin=low_ci, ymax=high_ci, fill=framework)) +
          geom_bar(stat="identity", width=0.5) +
          geom_errorbar(width = 0.25) +
          theme_minimal(base_family="Source Sans Pro") +
          scale_fill_manual(values=framework_colors) +
          labs(title = "Speed of Text Generation via Custom Keras Model",
               x = "Keras Backend",
               y = "Average Runtime per Epoch (seconds)",
               fill = "")

plot %>% ggplotly(tooltip=c("x", "y"))
```

CNTK is **`r (df_speed$mean[2] / df_speed$mean[1]) %>% round(2)`**x the speed of TensorFlow.